Detecting Facial Expressions in Professional Tennis Matches

### 2017-07-28 Report06-12.Rmd
Line for figures not images folder
moved blocks of text to subsections of results

    #read in image
    #image <- readImage(paste0("figures/", i))
    #used in analyses
    image <- readImage(paste0("images/", i))

@@

In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcasted videos of elite tennis matches. Using the broadcasted videos gives an objective insight to emotions as the player progresses through a match.
While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software. As opposed to the approach of previous studies that have used Player's recollections after a game to determine their emotions.

@@

##Manual Annotation
To record the details of attributes for each face and scene a Shiny [-@shiny] App was created. We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R]. This helped to provide information for all attributes quickly and consistently.

@@

@@

\newpage
# Results

@@

@@

\newpage

@@

All the potential facees that Google found which do not match manually annotated faces were correctly identifying faces.

\newpage

@@

## Results Overview
Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections. This would be a strong incentive to use Google for facial recognition in sports application. 
It was considered that Google's API may have been finding more unwanted faces than the other APIs.
Table \@ref(tab:Type-Matches-Manual) details the amounts of faces that were found by each API that matched or did not match a face found manually. There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
This was unexpected as it was presumed that majority of the faces annotated manually would be found.

Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd memebers were beyond what would be expected of an emotion recognition application for tennis players. These were deemed unlikely to be detected and neglected during manual annotation.

@@

>>>>

    #read in image
    image <- readImage(paste0("figures/", i))
    #used in analyses
    #image <- readImage(paste0("images/", i))

@@

In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcast videos of elite tennis matches. Using the broadcast videos gives an objective insight to emotions as the player progresses through a match.
While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software. As opposed to the approach of previous studies that have used Player's recollections after a game to determine their emotions.

@@

##Manual Annotation
To record the details of attributes for each face and scene a Shiny [@shiny] App was created. We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R]. This helped to provide information for all attributes quickly and consistently.

@@

COMMENT: Add a paragraph on time taken to find faces for each software

@@

# Results

@@

Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections. This would be a strong incentive to use Google for facial recognition in sports application. 
It was considered that Google's API may have been finding more unwanted faces than the other APIs.
Table \@ref(tab:Type-Matches-Manual) details the amounts of faces that were found by each API that matched or did not match a face found manually. There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
This was unexpected as it was presumed that majority of the faces annotated manually would be found.

@@

@@

Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players. These were deemed unlikely to be detected and neglected during manual annotation.

All the potential faces that Google found which do not match manually annotated faces were correctly identifying faces.

@@

## Results Overview

@@

# Acknowledgements

COMMENT: Add your software and data file list here, list packages used here, e.g. The R package ggplot2 [@ggplot2] was used to make the plots.
